Hunting experience and prey behaviour shape individual foraging specialisation in a predator-prey videogame

### 2023-01-31 manuscript/Chapter2-manuscript.Rmd
updated MS (need to update results text)

---
title: "Experience and prey behaviour jointly shape individual foraging specialisation and success in a predator-prey videogame"
output: 
  word_document:
    reference_docx: Chapter2-styles.docx
    fig_caption: yes
    pandoc_args: ["-Fpandoc-crossref"] # to have eq. numbers
bibliography: references.bib
csl: e-letters.csl
---

@@

library(data.table)
library(brms)
library(flextable)
library(officer)
library(tidyr)

@@

```{r}
#\[
#\begin{align}
#logit (P_{i}) &= (\beta_{0} + id_{0,i}) \\
#&\text{ } + \text{ } \beta_{1} \textit{match duration}_{i} \\
#&\text{ } + \text{ } f(\textit{cumulative xp}_{i}) \\
#\end{align}
#\tag{1}
#\]
```

@@

```{r table1, ft.align = "left"}

tab1 <- readRDS(here::here("outputs", "05_outputs_tables", "05_table1.rds"))

tab1 <- autofit(tab1)

tab1 <- tab1 %>% 
  footnote(
    i = 1, j = 1,
    part = "header",
    value = as_paragraph(
      "* 'elpd' refers to the 'expected log pointwise density' and is the value chosen to select the best model"),
    ref_symbols = " "
  ) %>%
  fontsize(size = 11, part = "all") %>%
  font(fontname = "Times New Roman", part = "all")

set_caption(
  tab1,
  caption = "Leave-one-out cross-validation table of the three hierarchical GAMMs relating hunting success to player experience.",
  style = "Table Caption"
)

@@

tab2 <- tab2 %>% 
  footnote(
    i = 1, j = 1,
    part = "header",
    value = as_paragraph(
      "* We applied the exponent to the intercept values of sigma parameters, estimated on a log scale, and then squared them, such that values are mean posterior residual variances. We back-transformed the hunting success values, estimated on a logit scale, back to a probability scale."),
    ref_symbols = " "
  ) %>%
  font(fontname = "Times New Roman", part = "all") %>%
  width(j = c(1:5), width = 3.7, unit = "cm")

set_caption(
  tab2,
  caption = "Posterior mean estimates and 95% credible intervals computed by the multivariate double-hierarchical generalized linear model of predator speed, prey speed, and predator hunting success.",
  style = "Table Caption"
)

@@

@@

At all experience levels, predators that were on average faster (mean) were also travelling faster in all their matches (IIV) ($cor_{novice}$ = `r toString(format(cor_tab[1,2]))` [`r toString(format(cor_tab[1,3]))`, `r toString(format(cor_tab[1,4]))`], $cor_{interm}$ = `r toString(format(cor_tab[6,2]))` [`r toString(format(cor_tab[6,3]))`, `r toString(format(cor_tab[6,4]))`], $cor_{adv}$ = `r toString(format(cor_tab[15,2]))` [`r toString(format(cor_tab[15,3]))`, `r toString(format(cor_tab[15,4]))`]) (i.e. they were more specialized at travelling fast). Thus, slower predators were also more flexible in their movement through time (Figure 3). In general, predators tended to be faster (mean) when they encountered prey that were on average faster (mean) ($cor_{novice}$ = `r toString(format(cor_tab[16,2]))` [`r toString(format(cor_tab[16,3]))`, `r toString(format(cor_tab[16,4]))`], $cor_{interm}$ = `r toString(format(cor_tab[31,2]))` [`r toString(format(cor_tab[31,3]))`, `r toString(format(cor_tab[31,4]))`], $cor_{adv}$ = `r toString(format(cor_tab[50,2]))` [`r toString(format(cor_tab[50,3]))`, `r toString(format(cor_tab[50,4]))`]) (Figure 4). At the three experience levels, there were only weak correlations between predator IIV and mean prey speed ($cor_{novice}$ = `r toString(format(cor_tab[17,2]))` [`r toString(format(cor_tab[17,3]))`, `r toString(format(cor_tab[17,4]))`], $cor_{interm}$ = `r toString(format(cor_tab[32,2]))` [`r toString(format(cor_tab[32,3]))`, `r toString(format(cor_tab[32,4]))`], $cor_{adv}$ = `r toString(format(cor_tab[51,2]))` [`r toString(format(cor_tab[51,3]))`, `r toString(format(cor_tab[51,4]))`]) (Figure 3). Similarly, predators specialized in a faster foraging mode (IIV) when encounters with prey were more predictable (IIV) ($cor_{novice}$ = `r toString(format(cor_tab[23,2]))` [`r toString(format(cor_tab[23,3]))`, `r toString(format(cor_tab[23,4]))`], $cor_{interm}$ = `r toString(format(cor_tab[40,2]))` [`r toString(format(cor_tab[40,3]))`, `r toString(format(cor_tab[40,4]))`], $cor_{adv}$ = `r toString(format(cor_tab[61,2]))` [`r toString(format(cor_tab[61,3]))`, `r toString(format(cor_tab[61,4]))`]), but the correlations were weak (Figure 3). In the four cases described above, the correlations became stronger as predators gained experience (Figure 3).

@@

We did not detect strong correlations between the predators' average speed and hunting success ($cor_{novice}$ = `r toString(format(cor_tab[67,2]))` [`r toString(format(cor_tab[67,3]))`, `r toString(format(cor_tab[67,4]))`], $cor_{interm}$ = `r toString(format(cor_tab[81,2]))` [`r toString(format(cor_tab[81,3]))`, `r toString(format(cor_tab[81,4]))`], $cor_{adv}$ = `r toString(format(cor_tab[96,2]))` [`r toString(format(cor_tab[96,3]))`, `r toString(format(cor_tab[96,4]))`]), nor between the IIV in speed and hunting success ($cor_{novice}$ = `r toString(format(cor_tab[68,2]))` [`r toString(format(cor_tab[68,3]))`, `r toString(format(cor_tab[68,4]))`], $cor_{interm}$ = `r toString(format(cor_tab[82,2]))` [`r toString(format(cor_tab[82,3]))`, `r toString(format(cor_tab[82,4]))`], $cor_{adv}$ = `r toString(format(cor_tab[97,2]))` [`r toString(format(cor_tab[97,3]))`, `r toString(format(cor_tab[97,4]))`]), suggesting that both slower/flexible and faster/specialist predators were both equally successful (Figure 3). However, when predators were novice, there was a strong negative correlation between the average speed of the prey that they encountered and their hunting success ($cor_{novice}$ = `r toString(format(cor_tab[73,2]))` [`r toString(format(cor_tab[73,3]))`, `r toString(format(cor_tab[68,4]))`]). Hence, novice individuals that encountered faster prey were less successful. This relationship was decoupled at the later experience levels, such that encounters with faster prey at intermediate and advanced stages were not as strongly correlated with hunting success anymore ($cor_{interm}$ = `r toString(format(cor_tab[87,2]))` [`r toString(format(cor_tab[87,3]))`, `r toString(format(cor_tab[87,4]))`], $cor_{adv}$ = `r toString(format(cor_tab[102,2]))` [`r toString(format(cor_tab[102,3]))`, `r toString(format(cor_tab[102,4]))`]).

>>>>

---
title: "Hunting experience and prey behaviour shape individual foraging specialisation in a predator-prey videogame"
output: 
  word_document:
    reference_docx: Chapter2-styles.docx
    fig_caption: yes
    pandoc_args: ["-Fpandoc-crossref"] # to have eq. numbers
bibliography: references.bib
csl: e-letters.csl
---

@@

library(data.table)
library(brms)
library(flextable)
#library(officer)
library(tidyr)

@@

@@

@@

tab2 <- tab2 %>% 
  footnote(
    i = 1, j = 1,
    part = "header",
    value = as_paragraph(
      "* We applied the exponent to the parameter values for sigma (intercepts and predator ID), estimated on a log scale, such that values are mean posterior standard deviations (SD). We back-transformed the hunting success values, estimated on a logit scale, back to a probability scale."),
    ref_symbols = " "
  ) %>%
  font(fontname = "Times New Roman", part = "all") %>%
  width(j = c(1:5), width = 3.7, unit = "cm")

set_caption(
  tab2,
  caption = "Posterior mean estimates and 95% credible intervals computed by the multivariate double-hierarchical generalized linear model of predator speed, prey speed, and predator hunting success.",
  style = "Table Caption"
)
```

@@

```{r, eval=FALSE}

@@

At all experience levels, predators that were on average faster (mean) were also travelling faster in all their matches (IIV) (Figure 3-S1). Thus, faster predators specialized at travelling fast, while slower predators were more flexible in their movement through time. In general, predators tended to be faster (mean) when they encountered prey that were on average faster (mean) (Figure 3-S1). At the three experience levels, there were only weak correlations between predator IIV and mean prey speed (Figure 3-S1). Similarly, predators specialized in a faster foraging mode (IIV) when encounters with prey were more predictable (IIV), but the correlations were weak (Figure 3-S1). In the four cases described above, the correlations became stronger as predators gained experience (Figure 3-S1).

@@

We did not detect strong correlations between the predators' average speed and hunting success (Figure 3-S1), nor between the IIV in speed and hunting success (Figure 3-S1), suggesting that both slower/flexible and faster/specialist predators were both equally successful. However, when predators were novice, there was a strong negative correlation between the average speed of the prey that they encountered and their hunting success (Figure 3-S1). Hence, novice individuals that encountered faster prey were less successful. This relationship was decoupled at the later experience levels, such that encounters with faster prey at intermediate and advanced stages were not as strongly correlated with hunting success anymore (Figure 3-S1).
